\documentclass[12pt]{article}
\usepackage[nohead,margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{url}
\usepackage{color}
\usepackage{aas_macros}

\setlength{\parindent}{0cm}
\pagestyle{plain}
\renewcommand{\paragraph}[1]{\vskip 1.5ex\textbf{#1}\nopagebreak[4]\\[1ex]}
\renewcommand{\refname}{\normalsize Publications}

\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\header}[1]{\textbf{#1}}

\begin{document}
\title{Curriculum vitae}
\author{Roland Haas}
\date{}
\maketitle

\paragraph{Personal information}
\begin{tabular}{lp{0.75\linewidth}}
Name &
Roland Haas \\
Date of birth &
May 29th, 1980 \\
Nationality &
German, permanent resident of Canada \\
Languages &
English: fluent, German: native, French: basic \\
Mailing address &
TAPIR Mailcode 350-17 Caltech 1200 E California Blvd Pasadena, CA 91125 USA \\
Phone number &
(626) 395-6987 \\
Email &
\url{rhaas@tapir.caltech.edu} \\
Web &
\url{http://www.tapir.caltech.edu/~rhaas}
\end{tabular}

\paragraph{Education}
\begin{tabular}{llllp{3.2cm}}
&
\header{Topic} &
\header{Location} &
\header{Advisor} &
\header{Duration} \\
Postdoc &
Numerical Relativity &
Caltech &
Christian Ott &
09/2011 -- present \\
Postdoc &
\parbox{3cm}{Numerical\\Astrophysics} &
Georgia Tech &
Pablo Laguna &
08/2008 -- 09/2011 \\
Ph.D. &
Theoretical Physics &
University of Guelph &
Eric Poisson &
02/2005 -- 08/2008 \\
M.Sc. &
Theoretical Physics &
University of Guelph &
Eric Poisson &
09/2003 -- 02/2005 \\
Diplom &
Physics &
Universit\"at Konstanz &
 &
Incomplete (left for Guelph)\\
\end{tabular}

\paragraph{Research interests}
My main research interests lie in the field of computational astrophysics.
I am strongly interested in computational science,
especially numerical techniques applicable to general relativistic
magnetohydrodynamics. 
My research interests include aspects of analytical
relativity in particular black hole perturbation theory as well as
semi-analytical aspects thereof. 

I am strongly involved in the Einstein Toolkit
collaboration~\cite{2012CQGra..29k5001L} which aims to
provide an open source, stable, well maintained and documented code for 
general relativistic magnetohydrodynamics simulations.

\paragraph{Awards}
\textbf{NSERC Postdoctoral Fellowship} (2010 -- 2012)\\
\textbf{NSERC Postgraduate Scholarship} (2006)\\
\textbf{Governor General's Academic Medal} (2005)
Awarded by the Governor General to the student
graduating with the highest average from a university program. \\
\textbf{Ontario Graduate Scholarship} (2005)

\paragraph{Services}
\textbf{Referee} for PRD, PRL, and  CQG\\
\textbf{Session chair} Numerical Simulations of Black holes and Neutron Stars,
April APS meeting 2009, Washington DC. \\
\textbf{Co-Maintainer} of the Einstein Toolkit, a collaborative NSF funded
effort by LSU, RIT, Georgia Tech, and Caltech to provide robust simulation
codes for numerical relativity and numerical astrophysics.\\
\textbf{Organizer} of the relativity section of the weekly TAPIR seminars.

\paragraph{Lectures}
Tutorial session on writing an analysis module at the Spring Einstein Toolkit
workshop attached to the April APS meeting in Atlanta, 2012.\\
Tutorial session and introduction to the Einstein Toolkit at the Summer
Einstein Toolkit workshop at the Caltech Gravitational-Wave Astrophysics School 2013.

\paragraph{Invited talks}
``Gravitational and electromagnetic signatures from the tidal disruption of
stars'', Caltech, Pasadena. CaJAGWR Seminars.\\
``Three-Dimensional General-Relativistic Hydrodynamic Simulations of Binary
Neutron Star Coalescence and Stellar Collapse with Multipatch Grids'', UIUC,
Urbana. Theoretical Astrophysics and General Relativity Seminar.

\paragraph{Grants}
\textbf{Co-principal investigator} of NSF XRAC grant TG-PHY100033 ``Simulations
of Relativistic Astrophysical Systems''\\
\textbf{Co-principal investigator} of NERSC project m152 ``Central Engine Models for Core-Collapse Supernovae and Long Gamma-Ray
Bursts''\\

\paragraph{Students mentored}
\textbf{Jeffrey Kaplan} Graduate Student. Project: binary neutron star
inspirals with SpEC.\\
\textbf{Jonas Lippuner} Graduate Student. Project: binary neutron star
inspirals with SpEC.\\
\textbf{Sherwood Richers} Graduate Student. Project: Neutrino Transport in
Supernova Simulations.\\
\textbf{Hannah Klion} Summer Undergraduate Research Fellowship
(SURF) student in 2012, now working as an undergraduate researcher with the
group. Project: Gravitational Waves from Rapidly Rotating Core-Collapse
Supernovae.\\
\textbf{Cheol Woo (Peter) Park} Summer Undergraduate Research Fellowship
(SURF) student in 2012. Project: black hole perturbation theory and white
dwarf disruption by an intermediate mass black hole.\\
\textbf{Cutter Coryell} Summer Undergraduate Research Fellowship
(SURF) student in 2013. Project: Testing Fully Dynamical Adaptive Mesh
Refinement in the Einstein Toolkit.


%.!gawk '/^@ARTICLE{/{print "\\nocite{"gensub("@ARTICLE{","","",gensub(",$","","",$0))"}"}' rhaaspub.bib 
\nocite{2013arXiv1307.3476V}
\nocite{2013ApJ...769...85S}
\nocite{2013ApJ...768..115O}
\nocite{2013arXiv1304.7787R}
\nocite{2013arXiv1304.5544M}
\nocite{2013PhRvD..87d1501Z}
\nocite{2012arXiv1212.4837S}
\nocite{2012arXiv1212.1191R}
\nocite{2012arXiv1210.6674O}
\nocite{2012PhRvD..86b4026O}
\nocite{2012CQGra..29k5001L}
\nocite{2012ApJ...749..117H}
\nocite{2012ApJ...744...45B}
\nocite{2011arXiv1112.3928H}
\nocite{2011arXiv1112.3707H}
\nocite{2011CQGra..28i4020B}
\nocite{2010ApJ...715.1117B}
\nocite{2007PhRvD..75l4011H}
\nocite{2006PhRvD..74d4009H}
\nocite{2005CQGra..22S.739H}
\nocite{2013arXiv1307.5307T}
\nocite{Haas:nsns}
\newpage
\bibliographystyle{hunsrt}
\bibliography{rhaaspub}

\end{document}

