%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,letterpaper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('letterpaper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvcolor{orange}                             % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Roland}{Haas}
\title{Curriculum vitae}                           % optional, remove / comment the line if not wanted
\address{Department of Physics \& Astronomy\\
Vancouver Campus\\
325 - 6224 Agricultural Road\\
Vancouver, BC V6T 1Z1 \\}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\email{rhaas@mail.ubc.ca}                    % optional, remove / comment the line if not wanted
\homepage{www.phas.ubc.ca/\textasciitilde rhaas}            % optional, remove / comment the line if not wanted
\social[linkedin]{roland-haas}                         % optional, remove / comment the line if not wanted
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[bitbucket]{rhaas80}                           % optional, remove / comment the line if not wanted
\social[github]{rhaas80}                           % optional, remove / comment the line if not wanted
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted


% AASTeX journal abbrevs
\newcommand\aj{\textrm{AJ}}%        % Astronomical Journal 
\newcommand\araa{\textrm{ARA\&A}}%  % Annual Review of Astron and Astrophys 
\newcommand\apj{\textrm{ApJ}}%    % Astrophysical Journal 
\newcommand\apjl{\textrm{ApJL}}     % Astrophysical Journal, Letters 
\newcommand\apjs{\textrm{ApJS}}%    % Astrophysical Journal, Supplement 
\newcommand\ao{\textrm{ApOpt}}%   % Applied Optics 
\newcommand\apss{\textrm{Ap\&SS}}%  % Astrophysics and Space Science 
\newcommand\aap{\textrm{A\&A}}%     % Astronomy and Astrophysics 
\newcommand\aapr{\textrm{A\&A~Rv}}%  % Astronomy and Astrophysics Reviews 
\newcommand\aaps{\textrm{A\&AS}}%    % Astronomy and Astrophysics, Supplement 
\newcommand\azh{\textrm{AZh}}%       % Astronomicheskii Zhurnal 
\newcommand\baas{\textrm{BAAS}}%     % Bulletin of the AAS 
\newcommand\icarus{\textrm{Icarus}}% % Icarus
\newcommand\jaavso{\textrm{JAAVSO}}  % The Journal of the American Association of Variable Star Observers
\newcommand\jrasc{\textrm{JRASC}}%   % Journal of the RAS of Canada 
\newcommand\memras{\textrm{MmRAS}}%  % Memoirs of the RAS 
\newcommand\mnras{\textrm{MNRAS}}%   % Monthly Notices of the RAS 
\newcommand\pra{\textrm{PhRvA}}% % Physical Review A: General Physics 
\newcommand\prb{\textrm{PhRvB}}% % Physical Review B: Solid State 
\newcommand\prc{\textrm{PhRvC}}% % Physical Review C 
\newcommand\prd{\textrm{PhRvD}}% % Physical Review D 
\newcommand\pre{\textrm{PhRvE}}% % Physical Review E 
\newcommand\prl{\textrm{PhRvL}}% % Physical Review Letters 
\newcommand\pasp{\textrm{PASP}}%     % Publications of the ASP 
\newcommand\pasj{\textrm{PASJ}}%     % Publications of the ASJ 
\newcommand\qjras{\textrm{QJRAS}}%   % Quarterly Journal of the RAS 
\newcommand\skytel{\textrm{S\&T}}%   % Sky and Telescope 
\newcommand\solphys{\textrm{SoPh}}% % Solar Physics 
\newcommand\sovast{\textrm{Soviet~Ast.}}% % Soviet Astronomy 
\newcommand\ssr{\textrm{SSRv}}% % Space Science Reviews 
\newcommand\zap{\textrm{ZA}}%       % Zeitschrift fuer Astrophysik 
\newcommand\nat{\textrm{Nature}}%  % Nature 
\newcommand\iaucirc{\textrm{IAUC}}% % IAU Cirulars 
\newcommand\aplett{\textrm{Astrophys.~Lett.}}%  % Astrophysics Letters 
\newcommand\apspr{\textrm{Astrophys.~Space~Phys.~Res.}}% % Astrophysics Space Physics Research 
\newcommand\bain{\textrm{BAN}}% % Bulletin Astronomical Institute of the Netherlands 
\newcommand\fcp{\textrm{FCPh}}%   % Fundamental Cosmic Physics 
\newcommand\gca{\textrm{GeoCoA}}% % Geochimica Cosmochimica Acta 
\newcommand\grl{\textrm{Geophys.~Res.~Lett.}}%  % Geophysics Research Letters 
\newcommand\jcp{\textrm{JChPh}}%     % Journal of Chemical Physics 
\newcommand\jgr{\textrm{J.~Geophys.~Res.}}%     % Journal of Geophysics Research 
\newcommand\jqsrt{\textrm{JQSRT}}%   % Journal of Quantitiative Spectroscopy and Radiative Trasfer 
\newcommand\memsai{\textrm{MmSAI}}% % Mem. Societa Astronomica Italiana 
\newcommand\nphysa{\textrm{NuPhA}}%     % Nuclear Physics A 
\newcommand\physrep{\textrm{PhR}}%       % Physics Reports 
\newcommand\physscr{\textrm{PhyS}}%        % Physica Scripta 
\newcommand\planss{\textrm{Planet.~Space~Sci.}}%  % Planetary Space Science 
\newcommand\procspie{\textrm{Proc.~SPIE}}%      % Proceedings of the SPIE 

\newcommand\actaa{\textrm{AcA}}%  % Acta Astronomica
\newcommand\caa{\textrm{ChA\&A}}%  % Chinese Astronomy and Astrophysics
\newcommand\cjaa{\textrm{ChJA\&A}}%  % Chinese Journal of Astronomy and Astrophysics
\newcommand\jcap{\textrm{JCAP}}%  % Journal of Cosmology and Astroparticle Physics
\newcommand\na{\textrm{NewA}}%  % New Astronomy
\newcommand\nar{\textrm{NewAR}}%  % New Astronomy Review
\newcommand\pasa{\textrm{PASA}}%  % Publications of the Astron. Soc. of Australia
\newcommand\rmxaa{\textrm{RMxAA}}%  % Revista Mexicana de Astronomia y Astrofisica

%% added feb 9, 2016
\newcommand\maps{\textrm{M\&PS}}% Meteoritics and Planetary Science
\newcommand\aas{\textrm{AAS Meeting Abstracts}}% American Astronomical Society Meeting Abstracts
\newcommand\dps{\textrm{AAS/DPS Meeting Abstracts}}% American Astronomical Society/Division for Planetary Sciences Meeting Abstracts


% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Professional Experience}
\cventry{04/2025--current}{Scientific Software Developer}{CHIME, University of British Columbia}{Vancouver, BC}{}{Computational Astronomy}
\cventry{07/2016--04/2025}{Senior research programmer}{National Center for Supercomputing Applications, University of Illinois}{Urbana, IL}{}{Numerical Relativity}
\cventry{09/2014--07/2016}{Junior scientist / Postdoc}{Albert Einstein Insititute}{Potsdam}{Advisor: Alessandra Buonanno}{Numerical Relativity}
\cventry{09/2011--08/2014}{Postdoctoral research fellow}{Caltech}{Pasadena}{Advisor: Christian Ott}{Numerical Relativity}
\cventry{08/2008--09/2011}{Postdoctoral research fellow}{Georgia Tech}{Atlanta}{Advisor: Pablo Laguna}{Numerical astrophysics}

\section{Education}
\cventry{12/2005--08/2008}{PhD in physics}{University of Guelph}{Guelph}{}{
  \emph{Self-force on point particles in orbit around a Schwarzschild black hole}\\
  Advisor: Eric Poisson}
\cventry{09/2003--12/2005}{MSc in physics}{University of Guelph}{Guelph}{}{
  \emph{Mass loss of a scalar charge in cosmological spacetimes}\\
  Advisor: Eric Poisson}
\cventry{09/1999-09/2003}{Diplom in physics}{Universitaet
Konstanz}{Konstanz}{Germany}{unfinished, left for Canada}
\cventry{09/1990 --08/1999}{High school}{Scheffel Gymnasium}{Lahr}{Germany} {}

\section{Research Interests and Areas}
\cvlistitem{Numerical relativity}
\cvlistitem{Relativistic (magneto-)hydrodynamics}
\cvlistitem{Extreme mass ratio inspirals and self-force problems}
\cvlistitem{Black hole perturbation theory}
\cvlistitem{Gravitational and electromagnetic emission from mixed black
hole—star systems}
\cvlistitem{The Einstein Toolkit}
\cvlistitem{Numerical techniques for mesh refinement, and elliptic problems}

\section{Grants and Awards}
\subsection{Research grants}
\cvitem{08/2024--current}{Principal investigator of NSF OAC grant 2411068
``E=mc2 - Enabling Multimessenger astrophysics through Community-driven
Cyberinfrastructure'' (USD 3,369,101, 4 yrs)}

\cvitem{07/2023--current}{Co-Principal investigator of NSF OAC grant 2310548
``Elements: An initial value solver for the era of multi-messenger
astrophysics'' (USD 597,233, 3 yrs)}

\cvitem{04/2020--current}{Principal investigator of NSF OAC grant 2004879
``The Einstein Toolkit ecosystem: Enabling fundamental research in the era of
multi-messenger astrophysics'' (USD 683,514, 4 yrs)}

\cvitem{07/2016--06/2022}{Co-principal investigator of NSF OAC grant 1550514
``Einstein Toolkit Community Integration and Data Exploration'' (USD 450,000, 6 yrs)}

\subsection{Computer time grants}
\cvitem{10/2020--current}{Principal investigator of NSF XRAC grant TG-PHY160053
``Convergence of Numerical Relativity and Deep Learning for Gravitational Wave
Astrophysics'' (USD 406,798, ongoing)}

\cvitem{06/2016--12/2021}{Blue Waters ``Illinois'' allocations (USD 2.0 million)}

\subsection{Awards and fellowships}
\cvitem{2010--2012}{NSERC postdoctoral Fellowship  (USD 80,000)}
\cvitem{2006--2008}{NSERC postgraduate scholarship  (CAD 41,000)}
\cvitem{2005}{Ontario Graduate Scholarship  (CAD 15,000)}
\cvitem{2005}{Governor General's Academic Medal {\small\emph{Awarded by the
Governor General to the student graduating with the highest average from a
university program}}}

\section{Presentations}
\cvitem{06/2024}{Presenter, North American Einstein Toolkit Workshop 2024,
Louisiana State University, Baton Rouge, LA}

\cvitem{07/2023}{Presenter, Einstein Toolkit Summer School,
Rochester Institute of Technology, Rochester, NY}

\cvitem{06/2022}{Presenter, Einstein Toolkit Summer School,
University of Idaho, Moscow, ID}

\cvitem{08/2020}{Presenter, North American Einstein Toolkit Workshop,
Louisiana State University, Baton Rouge, LA}

\cvitem{09/2019}{Presenter, European Einstein Toolkit Meeting, King's College
London, London, UK}

\cvitem{06/2019}{Presenter, North American Einstein Toolkit workshop,
Rochester Institute of Technology, Rochester, NY}

\cvitem{09/2018}{Presenter, European Einstein Toolkit Workshop,
University of Lisbon, Lisbon, Portugal}

\cvitem{07/2018}{Presenter,
North American Einstein Toolkit workshop, Georgia Tech, Atlanta, GA}

\cvitem{06/2018}{Presenter,
Mexican Einstein Toolkit school, Tecnológico de Monterrey, Guadalajaraa}

\cvitem{10/2017}{Presenter, EU Einstein Toolkit 2017 \& EdFest, Universitat de
les Illes Balears, Palma}

\cvitem{02/2017}{Participant, Workshop on MHD method in the Einstein Toolkit,
Columbia University, New York, NY}

\cvitem{06/2016}{Participant, Einstein Toolkit EU School and Workshop,
University of Trento, Trento}

\cvitem{08/2015}{Participant, ET Workshop 2015, University of Stockholm,
Stockholm}

\cvitem{10/2012}{Participant, ET Workshop Fall, Rochester Institute of
Technology, Rochester, NY}

\cvitem{04/2012}{Presenter, the EinsteinToolkit workshop at
the APS meeting in Atlanta}

\section{Academic Service}
\subsection{Conference and summer schools}

\cvitem{06/2023}{Co-Organizer, North American Einstein Toolkit Workshop,
Louisiana State University, Baton Rouge, LA}

\cvitem{07/2023}{Lead organizer, Einstein Toolkit CSSI Working Workshop,
Rochester Institute of Technology, Rochester, NY}

\cvitem{07/2022}{Lead organizer, Einstein Toolkit CSSI Working Workshop,
University of Illinois, Urbana, IL}

\cvitem{06/2022}{Co-organizer, Einstein Toolkit Summer School,
University of Idaho, Moscow, ID}

\cvitem{07/2021}{Lead organizer, Einstein Toolkit Summer School, University of
Illinois, Urbana, IL}

\cvitem{09/2019}{Scientific organization committee member,
European Einstein Toolkit Meeting, King's College London, London, UK}

\cvitem{10/2018}{Co-organizer, Deep Learning for Multimessenger Astrophysics:
Real-time Discovery at Scale workshop, University of Illinois, Urbana, IL}

\cvitem{07/2018}{Scientific organization committee member,
North American Einstein Toolkit workshop, Georgia Tech, Atlanta, GA}

\cvitem{06/2018}{Organization committee member,
Mexican Einstein Toolkit school, Tecnológico de Monterrey, Guadalajaraa}

\cvitem{07/2017}{Lead organizer of the EinsteinToolkit workshop at the NCSA /
UIUC meeting in Urbana-Champaign}

\cvitem{07/2015}{Local organizing committee member, CGWAS Caltech
Gravitatioanl Wave Astrophysics School, Caltech, Pasadena, CA}

\cvitem{06/2014}{Co-organizer, Capra Meeting on Radiation Reaction in General
Relativity, Caltech, Pasadena, CA}

\cvitem{07/2013}{Organizer of the Einstein Toolkit Summer Workshop at Caltech,
where all maintainer met to discuss future directions of the project.}

\cvitem{07/2013}{Local organizing committee member and presenter, CGWAS Caltech
Gravitatioanl Wave Astrophysics School, Caltech, Pasadena, CA}

\cvitem{2012--2014}{Organizer of the relativity section of the weekly TAPIR
seminars.}

\cvitem{04/2012}{Co-organizer of the EinsteinToolkit workshop at
the APS meeting in Atlanta}

\cvitem{04/2009}{Session chair Numerical Simulations of Black holes and
Neutron Stars, April APS meeting, Washington DC.}

\cvitem{2008--current}{Maintainer of the Einstein Toolkit, a collaborative NSF
funded effort by LSU, NCSA, RIT, Georgia Tech, and Caltech to provide robust
simulation codes for numerical relativity and numerical astrophysics.}

\subsection{Generic}
\cvitem{02/2023--current}{NCSA representative on OpenMP Architecture review board}
\cvitem{10/2016}{Observer, ExaHyPE consortium meeting, LRZ,  Garching}

\subsection{Reviewer}
\cvitem{2016--current}{Reviewer NSF, STFC}
\cvitem{2007--current}{Referee for JOSS, PRD, PRL, and CQG.}

\section{Software}
\cvlistitem{``Einstein Toolkit'', \url{https://einsteintoolkit.org}, lead PI since 2019}
\cvlistitem{``Cactus Computational Toolkit'', \url{https://cactuscode.org}}
\cvlistitem{``Carpet mesh refinement driver'', \url{https://github.com/EinsteinToolkit/Carpet}}
\cvlistitem{``CarpetX mesh refinement driver'', \url{https://github.com/EinsteinToolkit/CarpetX}}
\cvlistitem{``Outflow'', \url{https://github.com/rhaas80/Outflow}}
\cvlistitem{``ReadInterpolate'', \url{https://github.com/rhaas80/ReadInterpolate}}
\cvlistitem{``GRHydro'', \url{https://bitbucket.org/einsteintoolkit/einsteinevolve}}
\cvlistitem{``IllinoisGRMHD'', \url{https://bitbucket.org/zach_etienne/wvuthorns}}
\cvlistitem{``Simulation Factory'', \url{https://bitbucket.org/simfactory/simfactory2}}
\cvlistitem{``Eccentricity reduction for NR simulations'', \url{https://github.com/ncsagravity/eccred}}
\cvlistitem{``SpEC'', \url{https://www.black-holes.org/code/SpEC.html}}
\cvlistitem{``mpitar'', \url{https://git.ncsa.illinois.edu/rhaas/mpitar}}
\cvlistitem{``parfu'', \url{https://github.com/ncsa/parfu_archive_tool}}
\cvlistitem{``pa\_volume'', \url{https://github.com/rhaas80/pa_volume}}
\cvlistitem{Einstein Toolkit Summer School 2021 website, \url{https://github.com/EinsteinToolkit/et2021uiuc}}
\cvlistitem{Einstein Toolkit CI testing service, \url{https://github.com/EinsteinToolkit/tests/tree/scripts}}

\section{Memberships}
\cvitem{2025--current}{CHIME collaboration}
\cvitem{2018--current}{Associate member, LISA Science Collaboration}
\cvitem{2016--current}{Association for Computing Machinery}
\cvitem{2018--2021}{Full member, LISA Science Collaboration}
\cvitem{2014--2021}{Deutsche Physikalische Gesellschaft}
\cvitem{2011--2020}{Member, LIGO Science Collaboration}
\cvitem{2011--current}{Simulating eXtreme Spacetimes}
\cvitem{2008--current}{Einstein Toolkit}
\cvitem{2008--current}{American Physical Society}

\section{Postdocs mentored}
\cvlistitem{Alexandru Dima. Postdoc. Numerical relativity.}
\cvlistitem{Deborah Ferguson. Postdoc. Numerical relativity and gravitational wave data analysis.}

\section{Students mentored}
\subsection{Graduate Students}
\cvlistitem{Annamalai P S. Graduate Student. Project: Light propagation and polarization effects in Kerr spacetime. University of Southern Denmark.}
\cvlistitem{Domnica Garzon. Graduate Student. Project: Higher order modes in gravitational waves of eccentric, precessing binary black hole mergers.}
\cvlistitem{Semih Kacmaz. Graduate Student. Project: Machine learning-driven conservative-to-primitive conversion.}
\cvlistitem{Cheng-Hsin Cheng. Graduate Student. Project: Binary Black Hole Mergers in a Massive Scalar Field Cloud.}
\cvlistitem{Maxwell Rizzo. Graduate Students. Project: Initial data reader for COCAL in the Einstein Toolkit.}
\cvlistitem{Beyhan Karaka{\c s}. Graduate Student. Project: Effect of spin on binary neutron star mergers. University of Southampton.}
\cvlistitem{Yufeng Luo. Graduate Student. Project: Stability of rotating neutron stars. University of Wyoming.}
\cvlistitem{Shawn Rosofksy. Graduate Student. Project: binary neutron star inspirals with Cactus.}
\cvlistitem{Jonas Lippuner. Graduate Student. Project: binary neutron star inspirals with SpEC.}
\cvlistitem{Sherwood Richers. Graduate Student. Project: Neutrino Transport in Supernova Simulations.}
\cvlistitem{Jeffrey Kaplan. Graduate Student. Project: binary neutron star inspirals with SpEC.}

\subsection{Undergraduate Students}
\cvlistitem{Dhruv Srivastava. Undergraduate researcher in 2024.  Improving quality of Einstein Toolkit binary black hole simulations.}
\cvlistitem{Amrutaa Vibho. Undergraduate researcher in 2023 -- 2025. Numerical relativity simulations of eccentric binary black hole mergers.}
\cvlistitem{Chirag Maheshwari. Undergraduate researcher in 2023.  Automating simulation monitoring for the Einstein Toolkit.}
\cvlistitem{Ashley Turner. Undergraduate researcher in 2023.  Adding an OpenPMD reader module to VisIt visualization tool.}
\cvlistitem{Lisa Leung. Undergraduate researcher in 2022.  Improving quality of Einstein Toolkit binary black hole simulations.}
\cvlistitem{Hrishikesh Kalyanaraman. Undergraduate researcher in 2022.  Continuous integration testing for the Einstein Toolkit.} \cvlistitem{Nadine Kuo. Undergraduate researcher in 2022.  Continuous integration testing for the Einstein Toolkit.}
\cvlistitem{Parth Tiyagi. Undergraduate researcher in 2021. On the fly training data generation for large scale artificial neural network based gravitational waveform searches.}
\cvlistitem{Mingxin Li. Undergraduate researcher in 2021. Improving performance of characterizing numerical relativity waveforms.}
\cvlistitem{Mohammed Jamil. Undergraduate researcher in 2020. Using GitHub action for continuous integration testing of the Einstein Toolkit.}
\cvlistitem{Nuocheng Pan. Undergraduate researcher in 2020. Improving the robustness of the ENIGMA waveform generation code.}
\cvlistitem{Robert Nagel. Undergraduate researcher in 2020. Constructing a uniform framework to characterize numerical relativity waveforms.}
\cvlistitem{Yufeng Luo. Undergraduate researcher in 2019. DataVault an opens storage infrastructure for results obtained using the Einstein Toolkit.}
\cvlistitem{Kaiwen Zhang. Undergraduate researcher in 2019. Improving the quality of gravitational waves produced using the Einstein Toolkit.}
\cvlistitem{Joseph Adamo. Undergraduate researcher in 2019. Incorporating the ENIGMA gravitational wave model into LALsuite.}
\cvlistitem{Bridgette Davey. Undergraduate researcher (INCLUSION) in 2019.  Processing numerical relativity simulation results for use by LIGO.}
\cvlistitem{Brockton Brendal. Undergraduate researcher in 2019. Implementing methods to extrapolate gravitational waves to Scri+ in the NCSA POWER code.}
\cvlistitem{Bing-Jyun (Johnny) Tsao. Undergraduate researcher (SPIN) in 2019.  Solving the Poisson equation on irregular domains.}
\cvlistitem{Zeran Zhu. Undergraduate researcher (SPIN) in 2018. Generic output routines for the Einstein Toolkit.}
\cvlistitem{Sarah Habib. Undergraduate researcher (INCLUSION) in 2018, 2019.  Gauge invariant measurement of eccentricity in gravitational waves, implementing a method to reduce eccentricity in simulations using the Einstein Toolkit.}
\cvlistitem{Nicolas White. Undergraduate researcher (INCLUSION) in 2018.  Incorporating the ENIGMA gravitational wave model into LALsuite.}
\cvlistitem{Debopam Sanyal. Undergraduate researcher (SPIN) in 2018. Comparing methods to extrapolate gravitational waves to Scri+}
\cvlistitem{Vedant Puri. Undergraduate researcher (SPIN) in 2017. Testing Scheduled Jacobi Relaxation methods for use in the Einstein Toolkit.}
\cvlistitem{Sibo Wang. Undergraduate researcher (SPIN) in 2017. Project: Using the Adams-Bashforth timestepper in Cactus.}
\cvlistitem{Pablo Brubeck. Undergraduate research fellow in 2017. Project: Producing initial data for Cactus using LORENE.}
\cvlistitem{Nikita Jain. Undergraduate researcher (SPIN) in 2017. Project: A GPU accelerated BSSN using GAMER.}
\cvlistitem{Daniel Johnson. Undergraduate researcher in 2017. Python Open-source Waveform ExtractoR: An open source, python package to monitor and post-process numerical relativity simulations.}
\cvlistitem{Wei Ren. Undergraduate researcher in 2017. Project: Extrapolating gravitational waves produced by the Einstein Toolkit to Scri+.}
\cvlistitem{Dhara Mehta. Undergraduate researcher (SPIN) in 2017. Project: Automatically prune and archive simulation results produced by the Einstein Toolkit.}
\cvlistitem{Cutter Coryell. Summer Undergraduate Research Fellowship (SURF) student in 2013.  Project: Testing Fully Dynamical Adaptive Mesh Refinement in the Einstein Toolkit.}
\cvlistitem{Cheol Woo (Peter) Park. Summer Undergraduate Research Fellowship (SURF) student in 2012. Project: black hole perturbation theory and white dwarf disruption by an intermediate mass black hole.}
\cvlistitem{Hannah Klion. Summer Undergraduate Research Fellowship (SURF) student in 2012.  Project: Gravitational Waves from Rapidly Rotating Core-Collapse Supernovae.}

\pagebreak
\subsection{High-school Students}
\cvlistitem{Adam Rebei. Interning high-school student. Project: Effect of higher order modes in gravitational waves of eccentric binary black hole mergers.}

\section{Lectures}
\cvlistitem{Tutorial session on compiling the Einstein Toolkit at the Einstein Toolkit workshop at Lousiana State University, 2024.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Einstein Toolkit workshop at Rochester, 2023.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Einstein Toolkit workshop at Dublin, 2022.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Numerical Relativity Summer School at ICERM, 2022.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Einstein Toolkit workshop at UIdaho, 2022.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Einstein Toolkit workshop at LSU, 2020.}
\cvlistitem{Tutorial session on using the Einstein Toolkit at the Einstein Toolkit workshop at RIT, 2019.}
\cvlistitem{Tutorial session on using Python in HPC at the Blue Waters Symposium at Sunriver Resort, Sunriver, OR, 2019.}
\cvlistitem{Lecture on using MPI and OpenMP at the PIRE Winter School at the University of Arizona, 2018.}
\cvlistitem{Tutorial session on using adaptive mesh refinement at the EU Einstein Toolkit workshop in Lisbon, Portugal, 2018.}
\cvlistitem{Tutorial session on using Jupyter notebooks at the Blue Waters Symposium at Sunriver Resort, Sunriver, OR, 2018.}
\cvlistitem{Tutorial session on writing an analysis module at the Spring Einstein Toolkit workshop attached to the April APS meeting in Atlanta, 2012.}
\cvlistitem{Tutorial session and introduction to the Einstein Toolkit at the Summer Einstein Toolkit workshop at the Caltech Gravitational-Wave Astrophysics School 2013.}

\section{Invited talks}
\cvlistitem{``Using computational physics to study relativity and more'', University of Guelph, ON,  Colloquium presentation.  September, 2023. }
\cvlistitem{``Present and future astrophysics simulations using the Einstein Toolkit'', University of Wyoming, WY,  Colloquium presentation.  December, 2021. }
\cvlistitem{``Assessing confidence in numerical relativity waveforms of binary neutron star mergers'', Nikhef, Amsterdam, Netherlands. Seminar talk.  September, 2018. }
\cvlistitem{``Community astrophysics science with the Einstein Toolkit'', UIUC, Urbana-Champaign, IL. Theoretical Astrophysics and General Relativity Seminar.  September, 2017. }
\cvlistitem{``Update on binary neutron star merger simulations'', Goethe-University, Frankfurt, Germany. Astro coffee.  April, 2017.}
\cvlistitem{``Simulating multi-physics astrophysical problems using current and future codes'', Leibnitz Rechenzentrum, Garching, Germany. ExaHYPe collaboration meeting.  April, 2017. }
\cvlistitem{``Update on binary neutron star merger simulations'', Max-Planck-Institute for Gravitational Physics, Golm, Germany. AEI Seminar.  April, 2016. }
\cvlistitem{``Core collapse and binary neutron star inspiral simulation using multipatch grids'', University of Southampton, Southampton, UK. Gravity Seminar.  February, 2015.}
\cvlistitem{``Three-Dimensional General-Relativistic Hydrodynamic Simulations of Binary Neutron Star Coalescence and Stellar Collapse with Multipatch Grids'', UIUC, Urbana-Champaign, IL.  Theoretical Astrophysics and General Relativity Seminar. April, 2013. }
\cvlistitem{``Gravitational and electromagnetic signatures from the tidal disruption of stars'', Caltech, Pasadena, CA. CaJAGWR Seminars. April, 2012.}

\section{Contributed talks and posters}
\cvlistitem{``Astrophysics simulations using the Einstein Toolkit'', University of Illinois, Urbana-Champaign, IL. AstroFest, 2024}
\cvlistitem{``HydroOpenMPToy status'', King's College London, London, UK.  Einstein Toolkit Workshop. September, 2019}
\cvlistitem{``Deep Learning at Scale: A Paradigm Shift for Multi-Messenger Astrophysics'', Sunriver, Oregon. APS April Meeting. June, 2019}
\cvlistitem{``The NCSA eccentric gravitational waveform catalog'', Denver, CO. APS April Meeting. April, 2019}
\cvlistitem{``Multimessenger Astronomy at the University of Illinois'', Sunriver, Oregon. Blue Waters Symposium. June, 2018}
\cvlistitem{``Magnetic Field Amplification in Binary Neutron Star Merger Remnants'', Sunriver, Oregon. Blue Waters Symposium. June, 2018}
\cvlistitem{``Multimessenger Astronomy at the University of Illinois'', Sunriver, Oregon. Blue Waters Symposium. June, 2018}
\cvlistitem{``BOSS-LDG using Blue Waters for LIGO data analysis'',  Columbus, OH. APS April Meeting. April, 2018}
\cvlistitem{``Assessing confidence in numerical relativity waveforms of binary neutron star mergers'',  Columbus, Ohio. APS April Meeting. April, 2018}
\cvlistitem{``HydroOpenMPToy status'', University des Illes Baleares, Palma, Spain. Einstein Toolkit Workshop. October 2017.}
\cvlistitem{``Benchmarking Parallelized File Aggregation Tools for Large Scale Data Management'', Denver, CO. Supercomputing 2017, November 2017.}
\cvlistitem{``Neutron star simulations with SpEC'', University of Stockholm, Stockholm, Sweden. MICRA meeting. August, 2015}
\cvlistitem{``Postprocrocessing data in Cactus'', University of Stockholm, Stockholm, Sweden. Einstein Toolkit Workshop. June, 2015}
\cvlistitem{``Binary Neutron Star simulations using SpEC'', University of Thessaloniki, Thessaloniki, Greece. Workshop on Binary Neutron Star Mergers.  May, 2015}
\cvlistitem{``Binary Neutron Star simulations using SpEC'', UCSD, San Diego, CA. Pacific Coast Gravity Meeting. March, 2014}
\cvlistitem{``Binary Neutron Star simulations using SpEC'', Savannah, GA. APS April Meeting. April, 2014}
\cvlistitem{``Self-force driven inspiral of a scalar point particle into a Schwarzschild black hole'', UCLA, Los Angeles, CA. TASC Meeting 2013. December, 2013}
\cvlistitem{``Binary NS simulations using SpEC'', Uniwersytet Warszawski, Warsaw, Poland. Amaldi meeting. July, 2013}
\cvlistitem{``Binary NS simulations using SpEC'', Denver, CO. APS April Meeting. April, 2013}
\cvlistitem{``Binary NS simulations using SpEC'', UCD, Davis, CA. Pacific Coast Gravity Meeting. March, 2013}
\cvlistitem{``Binary NS simulations using SpEC'', Carnegie Observatories, Pasadena, CA. TASC Meeting 2012. November, 2012}
\cvlistitem{``Self-force driven inspiral of a scalar point particle into a Schwarzschild black hole: a progress report'', University of Maryland, Collega Park, MD. Capra Meeting on Radiation Reaction in General Relativity. June, 2012}
\cvlistitem{``Progress report: Binary NS simulations using SpEC'', Atlanta, GA. APS April Meeting. April, 2012}
\cvlistitem{``Self-force driven inspiral of a scalar point particle into a Schwarzschild black hole'', UCSB, Sata-Barbara, CA. Pacific Coast Gravity Meeting. March, 2012}
\cvlistitem{``Gravitational and Electromagnetic Signatures from the Tidal Disruption of a White Dwarf by an Intermediate Mass Black Hole'', Florida Atlantic University. Boca Raton, FL. Gulf Coast Gravity Meeting. May, 2011}
\cvlistitem{``Gravitational and Electromagnetic Signatures from the Tidal Disruption of a White Dwarf by an Intermediate Mass Black Hole'', Anaheim, CA.  APS April Meeting. May, 2011}
\cvlistitem{``Progress Report: Gravitational and Electromagnetic Signatures from Tidal Disruption of a White Dwarf by an Intermediate Mass Black Hole'', North Carolina State University, Raleigh, NC. Eastern Gravity Meeting. May, 2010}
\cvlistitem{``Gravitational and Electromagnetic Signatures from the Tidal Disruption of a White Dwarf by an Intermediate Mass Black Hole'', Washington, DC. APS April Meeting. February, 2010}
\cvlistitem{``Black Hole - Neutron Star Binary Simulations at Georgia Tech'', Louisiana State University, Baton Rouge, LA. Gulf Coast Gravity Meeting.  April, 2009}
\cvlistitem{``Electromagnetic self-force for eccentric orbits in Schwarzschild spacetime'', CNRS, Orleans, France. Capra meeting on Radiation Reaction, June, 2008}
\cvlistitem{``Electromagnetic self-force for eccentric orbits in Schwarzschild spacetime: A progress report'', St. Louis University, St Louis, MO. Midwest Relativity Meeting, November, 2007}
\cvlistitem{``Scalar self-force for eccentric orbits in Schwarzschild spacetime'', University of Alabama, Huntsville, AL. Capra meeting on Radiation Reaction, June, 2007}
\cvlistitem{``Scalar self-force for eccentric orbits in Schwarzschild spacetime'',  University of New Brunswick, Fredericton, NB. Canadian Conference on General Relativity and Relativistic Astrophysics, May, 2007}
\cvlistitem{``Scalar self-force for eccentric orbits in Schwarzschild spacetime'', Washington University, St Louis, MO. Midwest Relativity Meeting, November, 2006}

\begin{thebibliography}{99}
% https://ui.adsabs.harvard.edu/user/libraries/pzWebybvThCQyfOW6CVxrA
% https://ui.adsabs.harvard.edu/search/q=orcid%3A0000-0003-1424-6178&sort=date%20desc%2C%20bibcode%20desc/export-other
% format used:
% %ZEncoding:latex%ZLinelength:0\bibitem{%R} %5.3l, ``%T,'' %j, %V, %p (%Y).
\item[] \begin{tabular}{l@{\hspace{4ex}}r@{\hspace{4ex}}r@{\hspace{4ex}}r}
		&\href{https://www.scopus.com/authid/detail.uri?authorId=36084420600}{Scopus}
		&\href{https://scholar.google.com/citations?user=rZj1mR8AAAAJ}{Google Scholar}
		&\ldots since 2020\\
\hline
Citations	&4994	&7617	&4566\\
h-index		&38	&43	&34\\
i10-index	&N/A	&66	&63\\
\end{tabular}

legend: \underline{student supervised}, ($*$) - more than 100 citations
\input{allpub.tex}
\end{thebibliography}

\end{document}


%% end of file `template.tex'.

